Approval and participation indexes for a voting process

### 2015-04-24 ApresentacoesArtigos/collectiveRanking/paper.tex
terminada adicao da classificacao

The approval index $\alpha_i$ and the participation index $\gamma_i$ of the proposal $i$ was defined as:
\begin{equation}
\begin{split}
\alpha_i=\frac{v^+_i-v^-_i}{\eta_i} \\
\gamma_i=\frac{v^+_i+v^-_i}{\eta_i}
\end{split}
\end{equation}
where $v^+_i$, $v^-_i$ and $\eta_i$ are approval count, disapproval count and exhibition count, respectively.
Note that $\alpha_i\in[-1,1]$, $\gamma_i\in[0,1]$, and $\eta_i-v^+_i-v^-_i$ is the count of the ``indifferent'' manifestations received by proposal $i$.
Also, such $\alpha_i$ and $\gamma_i$ indexes are expected, for each proposal $i$, to be constants  plus a sampling estimate error that should be smaller as $\eta_i$ raises. This error is thought to be acceptable if $\eta_i$ is above a threshold $\overline{\eta}$ established by the participation community and public managers.
As an initial decision, the staff agreed to use $\overline{\eta}$ as to select $10-20\%$ of all proposals.
A threshold $\overline{\gamma}$ can be used as a required level of engagement for proposals to be relevant,
while the threshold $\overline{\alpha}$ is used to classify the outcome
as ``approved'',``disapproved'' and ``clash''. More specifically:

@@

If a proposal $i$ is both sampled and approved, than it is prioritized.
The coherent values of $\overline{\alpha_i}=0.5$ (or $1/3$)
and $\overline{\gamma_i}=0.5$ were chosen as standards of the decision model. 
These are likely to change with implementation and management.

>>>>

The approval index $\alpha_i$ and the participation index $\gamma_i$ of the proposal $i$ was defined as:
\begin{equation}
\begin{split}
\alpha_i=\frac{v^+_i-v^-_i}{\eta_i} \\
\gamma_i=\frac{v^+_i+v^-_i}{\eta_i}
\end{split}
\end{equation}
where $v^+_i$, $v^-_i$ and $\eta_i$ are approval count, disapproval count and exhibition count, respectively.
Note that $\alpha_i\in[-1,1]$, $\gamma_i\in[0,1]$, and $v^o_i=\eta_i-v^+_i-v^-_i$ is the count of the ``indifferent'' manifestations received by proposal $i$.
Also, such $\alpha_i$ and $\gamma_i$ indexes are expected, for each proposal $i$, to be constants  plus a sampling estimate error that should be smaller as $\eta_i$ raises. This error is thought to be acceptable if $\eta_i$ is above a threshold $\overline{\eta}$ established by the participation community and public managers.
As an initial decision, the staff agreed to use $\overline{\eta}$ as to select $10-20\%$ of all proposals.
A threshold $\overline{\gamma}$ can be used as a required level of engagement for proposals to be relevant,
while the threshold $\overline{\alpha}$ is used to classify the outcome
as ``approved'',``disapproved'' and ``clash''. More specifically:

@@

If a proposal is both sampled and approved, than it is prioritized.
The coherent values of $\overline{\alpha_i}=0.5$ (or $1/3$)
and $\overline{\gamma_i}=0.5$ were chosen as standards of the decision model. 
These are likely to change with implementation and management.
